Group 5 Report

### 2022-08-01 Report/Group 5 report.Rmd
edit intro

It is important to solve this problem because:
Creating KPI(s) is important for the organization’s performance 
management, to influence the objective, and to foster growth
Automating the data collection will streamline the work of OPX 
and create more transparency which enhances trust in charities

>>>>

It is important to solve this problem because:
1. Creating KPI(s) is important for the organization’s performance 
management, to influence the objective, and to foster growth
2. Automating the data collection will streamline the work of OPX 
and create more transparency which enhances trust in charities
